Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-27 paper.tex
Explain memory results for mmap

\subsection{\texttt{vm\_area\_struct}}

@@

\subsubsection{Memory (TODO: SPAI)}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures/mmap_mem_usage}
    \caption{$\Delta_i$ adjusted with control for benchmarks}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/vm_area_struct_count}
    \caption{Number of \texttt{vm\_area\_struct}s for benchmarks}
\end{figure}

>>>>

\subsection{\texttt{vm\_area\_struct}}
\label{ss_vm_area_struct}

@@

\subsubsection{Memory}
Figure \ref{fig:mmap\_mem\_usage} shows the growth in memory usage of the system
for the workloads described in section \ref{ss\_vm\_area\_struct}. The
\texttt{cont} workload coincides with the \texttt{control} workload as only the
first mmap operation allocates a \texttt{vm\_area\_struct}. The subsequent
operations are subsumed by the initial \texttt{vm\_area\_struct} as the mapped
regions are adjacent, and hence the memory usage does not increase despite the
large number of mmap operations.  The \texttt{stride} workload allocates a
\texttt{vm\_area\_struct} for each operation due to the separation of
allocations in the virtual address space. As a result, the memory usage
increases significantly as more memory is consumed with each mmap operation.
This is also the case for the \texttt{rand} workload which breaks up a single
\texttt{vm\_area\_struct} for a large area in the virtual address space into
multiple smaller areas, which results in the  allocation of a new structure for
every resize operation. The \texttt{rand} workload initially creates a new
\texttt{vm\_area\_struct} struct for each mmap operation. Eventually, these
allocations form larger contiguous allocations when two or more regions are
mapped next to each other, resulting in a single \texttt{vm\_area\_struct} being
used for that range. As a result, the memory usage begins to flatten out and
even decreases slightly as multiple \texttt{vm\_area\_struct}s are collapsed to
single structures. This is made clear by Figure \ref{fig:vm_area_struct_count}
which shows the growth \texttt{vm\_area\_struct} counts for each workload.
\begin{figure}
    \includegraphics[width=\columnwidth]{figures/mmap_mem_usage}
    \caption{$\Delta_i$ adjusted with control for benchmarks}
    \label{fig:mmap_mem_usage}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/vm_area_struct_count}
    \caption{Number of \texttt{vm\_area\_struct}s for benchmarks}
    \label{fig:vm_area_struct_count}
\end{figure}
